Approximation as Differentiation

### 2025-04-15 appendix/notes/grothendieck.tex
mathcal for metavariables that range over categories.

\begin{definition}[Grothendieck construction for $F$]
Suppose a functor $F: C \to \Cat$. The \emph{Grothendieck construction} $\Grothendieck{C}F$ for $F$ is the
category where:
\begin{itemize}
\item objects $X$ are pairs of an object $\idx{X}$ of $C$ and an object $\faml{X}$ of $F(\idx{X})$;
\item morphisms $f: X \to Y$ are morphisms $\idx{f}: \idx{X} \to \idx{Y}$ in $C$ paired with morphisms
$\faml{f}: F(f)(\faml{X}) \to \faml{Y}$ in $F(\idx{Y})$.
\end{itemize}
\end{definition}

>>>>

\begin{definition}[Grothendieck construction for $F$]
Suppose a functor $F: \cat{C} \to \Cat$. The \emph{Grothendieck construction} $\Grothendieck{\cat{C}}F$ for
$F$ is the category where:
\begin{itemize}
\item objects $X$ are pairs of an object $\idx{X}$ of $\cat{C}$ and an object $\faml{X}$ of $F(\idx{X})$;
\item morphisms $f: X \to Y$ are morphisms $\idx{f}: \idx{X} \to \idx{Y}$ in $C$ paired with morphisms
$\faml{f}: F(f)(\faml{X}) \to \faml{Y}$ in $F(\idx{Y})$.
\end{itemize}
\end{definition}
